Project Setup

### 2024-11-28 setup.qmd
Use appropriate callouts

::: {#wrn-legal-restrictions .callout-warning}
### Consider Legal Restrictions Before Sharing

@@

::: {#wrn-take-copyright-seriously .callout-warning}
### Take Copyright Seriously

>>>>

::: {#imp-legal-restrictions .callout-important}
### Consider Legal Restrictions Before Sharing

@@

::: {#imp-take-copyright-seriously .callout-important}
### Take Copyright Seriously
